### 2012-06-29 docs/makefiles/makefiles.tex
update to reflect recent changes

\noindent From {\tt extern}, we always include
\begin{itemize}
\item {\tt extern/model\_parser}
\item {\tt extern/LAPACK}
\item {\tt extern/random}
\item {\tt extern/BLAS}
\item {\tt \$\{EOS\_DIR\}}
\item {\tt \$\{NETWORK\_DIR\}}
\item {\tt \$\{CONDUCTIVITY\_DIR\}}
\end{itemize}
for most networks, we automatically add in {\tt extern/VODE} as well.

\noindent From {\tt MAESTRO/}, we add
\begin{itemize}
\item {\tt MAESTRO/constants}
\item {\tt MAESTRO/Source}
\end{itemize}
(although see the unit tests section below regarding {\tt MAESTRO/Source}.

>>>>

\noindent From {\tt Util}, we always include
\begin{itemize}
\item {\tt Util/model\_parser}
\item {\tt Util/random}
\end{itemize}

The microphysics, as described above is also included.  For the networks,
we include a file called {\tt NETWORK\_REQUIRES} into {\tt GMaestro.mak}
that tells us whether to also include {\tt Util/VODE} (if {\tt NEED\_VODE := t})
or {\tt Util/BLAS} (if {\tt NEED\_BLAS := t}).

From {\tt MAESTRO/}, we add
\begin{itemize}
\item {\tt MAESTRO/constants}
\item {\tt MAESTRO/Source}
\end{itemize}
(although see the unit tests section below regarding {\tt MAESTRO/Source}.
